Light inextensible strings under tension in the Schwarzschild geometry

### 2019-05-22 string_jpam.tex
further clarification pursuant to #16

\begin{figure}[p] % created by "closest_approach2.R"
\centering
\includegraphics[width=170mm]{closest_approach_selfintersecting.pdf}
\caption{Self-intersecting strings shown for $\phi\geq 0$.  Closest
  approach to the event horizon occurs at $\phi=0$ and
  $r\in\left(1,1.0761\right)$; strings are symmetrical about $\phi=0$}
\label{closest_approach_self_intersecting}
\end{figure}

>>>>

\begin{figure}[p] % created by "closest_approach2.R"
\centering
\includegraphics[width=170mm]{closest_approach_selfintersecting.pdf}
\caption{Self-intersecting strings shown for $\phi\geq 0$.  Closest
  approach to the event horizon occurs at $\phi=0$ (3 o'clock) and
  $r\in\left(1,1.0761\right)$; strings are symmetrical about $\phi=0$
  but for clarity only $\phi\geq 0$ is shown}
\label{closest_approach_self_intersecting}
\end{figure}
